### 2023-02-11 talk/talk.tex
a few typos and tweaks

MFO worksho on \\
Design and Analysis of Infectious Disease Studies
\\
Feb 23, 2023

@@

  We introduce the iterated block particle filter because it currently appears the most powerful algorithm available in \texttt{spatPomp}.

@@

  \begin{enumerate}
\item Combining measurement noise and process noise.
\item Including covariates in mechanistically plausible ways.
\item  Continuous time models.
\item  Modeling and estimating interactions in coupled systems.
\item  Dealing with unobserved variables.
\item  \myemph{Modeling spatial-temporal dynamics}.
\item  \myemph{Studying population dynamics via genetic sequence data}.
  \end{enumerate}

@@

  1--6 are from Bjornstad \& Grenfell ({\it Science}, 2001).\\
  7 is from Grenfell et al ({\it Science}, 2004).\\
  1--5 are largely solved, from a methodological perspective.

>>>>

MFO workshop on \\
Design and Analysis of Infectious Disease Studies
\\
Feb 23, 2023

@@

  \vspace{10mm}

  We introduce the {\bf iterated block particle filter} because it is currently the most powerful algorithm available in \texttt{spatPomp}.

@@

  \begin{enumerate}
\item Combining measurement noise and process noise.
\item Including covariates in mechanistically plausible ways.
\item  Continuous time models.
\item  Modeling and estimating interactions in coupled systems.
\item  Dealing with unobserved variables.
\item  \myemph{Modeling spatial-temporal dynamics}.
\item  Studying population dynamics via genetic sequence data.
  \end{enumerate}

@@

  1--6 are from Bjornstad \& Grenfell ({\it Science}, 2001).\\
  7 is an active topic, but not the focus of this talk.\\
  1--5 are largely solved, from a methodological perspective.
